---
title: 'Stats 250: Case Study 4 Report'
author: "Your Name"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

Thoroughly read through the assignment instructions (sent via email) and complete the required tasks using the document below.


***


## Data

The `pirates` data set: Every year, the town of Konstanz, Germany hosts the Annual International Pirating Meeting, where contemporary pirates, scallywags, miscreants, and rapscallions can revel in each other’s company. 

The pirate data set contains responses to a questionnaire given to attendees during the 2015 annual convention. The data below provide a description of each variable in the data.

1. `sex`: the pirate's self reported sex (female, male)
2. `age`: the pirate's self reported age (in years)
3. `height`: the pirate's self reported height (in cm)
4. `weight`: the pirate's self reported weight (in kg)
5. `headband`: a variable indicating whether the pirate wore a headband to the convention (yes or no)
6. `eyepatch`: a variable indicating whether the pirate wore an eyepatch to the convention (yes or no)
7. `college`: the "college" the pirate attended while at the convention (JSSPF or CCCC - see note below) 
8. `tattoos`: the number of tattoos the pirate sported while at the convention
9. `tchests`: secret treasure chests were hidden throughout the convention center during the annual conference. This variable indicates the number of treasure chests the pirate found during the conference.
10. `parrots`: an integer indicating the number of parrots the pirate claimed to have owned in his/her lifetime
11. `favorite.pirate`: the pirate’s self-reported favorite pirate throughout history (Anicetus, Blackbear, Edward Low, Hook, Jack Sparrow, Lewis Scot)
12. `sword.type`: the type of sword the pirate reported preferring to use during naval battles (banana, cutlass, sabre, scimitar)
13. `sword.time`: the time it takes (in seconds) the pirate to draw his/her sword, with smaller times being preferable!
14. `beard.length`: the pirate's beard length (in cm)
15. `grogg`: the number of mugs of "grogg" (which was made freely available to all conference attendees) that was consumed by the pirate.

Note: "JSSFP" stands for Jack Sparrow's School of Fashion and Piratery, while "CCCC" stands for Captain Chunk's Cannon Crew


Use the following code chunk to read in the data set. 

```{r read_data, include = FALSE}
load("pirates.rda")
```

And be sure to load any necessary packages!

```{r load_packages, include = FALSE}
library(ggplot2)
library(stats250package)
```



## Goal and Analysis

Propose a research question that you believe can be addressed using the available data.  

**Research Question**: Replace this text with your research question.



Use the code chunks below to complete your analysis. *Note: you might not use all of the code chunks below.* Feel free to delete excess code chunks or leave them in the document.

```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


\newpage

## Report

## 1. Description of Data

Replace this text with...




## 2. Research Question

Replace this text with...




## 3. Statistical Method

Replace this text with...




## 4. Analysis and Conclusions

Replace this text with...




\newpage

## Word Count

Self-report the word count of your report by following the steps below:

1. Highlight all of the text in the "Report" section above
2. In the top toolbar, click Edit > Word Count
3. Report the value of "Selected words" below

**Word Counts:** Replace this text with your word count


***


## Submission Instructions

Carefully follow the instructions below to properly submit your completed work.

1. At the top of the document, change the `author` field to your name. Do not change any of the other fields (title, date, output).

2. Click the **Knit** button.

3. Click on the file titled `casestudy04_report.pdf` in the bottom right window and confirm that your work has knitted properly. 

4. In the bottom right window, check the box next to `casestudy04_report.pdf`

5. Click More > Export. Note: you may see a gear icon instead of "More". 

6. Click Download and save the file to your computer. Do not change the name of the file ("casestudy04_report.pdf"). 

7. Head to *Canvas* and navigate to the corresponding assignment. Submit your `casestudy04_report.pdf` file!

Congratulations - you have completed the assignment!


